On the presentation of orthogonal groups over polynomial rings

### 2019-05-14 dl-paper.tex
Proving Lemma 26

 In the case $\alpha - \beta - \gamma \in \Phi$ we obtain from \eqref{Z2} of~\cref{Zrels} that
\[ z_{\gamma}(f, X\xi) ^ {x_{\beta-\alpha}(b)} = x_{\beta-\alpha} (- bXf\xi) \cdot x_{\gamma + \beta -\alpha} (N_{\gamma, \beta -\alpha}\cdot bf)     \cdot z_{\gamma}(f, X\xi)\ \text{if}\ \alpha - \beta - \gamma \in \Phi. \]
Notice that $\langle \gamma + \beta - \alpha, \alpha \rangle = 
  \langle \gamma , \alpha \rangle + \langle \beta , \alpha \rangle - \langle \alpha, \alpha \rangle \geq 1 + 1 - 2 = 0$, therefore the expression in the right-hand side is a product of generators of type 1, 2, 2 or 1, 3, 2. {\bf TODO: } Double check that both possibilities actually occur.

@@

>>>>

 In the case $\alpha - \beta - \gamma \in \Phi$ we obtain from \eqref{Z2} of~\cref{Zrels} that
\[ z_{\gamma}(f, X\xi) ^ {x_{\beta-\alpha}(b)} = x_{\beta-\alpha} (- bXf\xi) \cdot x_{\gamma + \beta -\alpha} (N_{\gamma, \beta -\alpha}\cdot bf)     \cdot z_{\gamma}(f, X\xi)\ \text{if}\ \alpha - \beta - \gamma \in \Phi. \]
 Notice that $\langle \gamma + \beta - \alpha, \alpha \rangle = \langle \gamma , \alpha \rangle + \langle \beta, 
 \alpha \rangle - \langle \alpha, \alpha \rangle \geq 1 + 1 - 2 = 0$, 
 therefore the expression in the right-hand side is a product of generators of type 1, 2, 2 or 1, 3, 2. {\bf TODO: } Double check that both possibilities actually occur.

@@

\begin{lemma}
 For $g \in K(A[X], M[X]) \cap P_\alpha(m) \cap P_\beta(m')$ holds 
 \[ x_{\beta - \alpha}(b) \cdot S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am)\cdot h_{\beta - \alpha}((1 + N_{\alpha,-\beta} \cdot abm')^{-1})\cdot x_{\beta - \alpha}(-b(1 + N_{\alpha,-\beta} \cdot abm')) \in P\left(\alpha, \frac{m - bm'}{1+am}\right). \]
\end{lemma}
\begin{proof}
Set $\epsilon = N_{\alpha, -\beta}$, $c = 1 + \epsilon a b m'$, $s_0 = \langle -a, m \rangle$, $s_1 = \langle -\epsilon am', -bc^{-1} \rangle$.
By~\cref{K-a-b} we can write $g = g_0 \cdot $ for some $m, m' \in M$ hence by ??? we obtain that
 \begin{multline} \nonumber 
 S_\alpha(a, x_{-\beta}(m'X) \cdot x_{-\alpha}(mX)) \cdot h_{\alpha}^{-1}(1+am)\cdot h_{\beta-\alpha}(c^{-1})\cdot x_{\beta - \alpha}(-bc) = \\ 
 = S_\alpha(a, x_{-\beta}(m'X)) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot h_\alpha^{-1} (1 + am) \cdot h_{\beta - \alpha}(c^{-1}) \cdot x_{\beta - \alpha}(-bc) = \\
 = x_{-\beta}(m'X) \cdot x_{\alpha - \beta}(\epsilon am') \cdot x_{\beta - \alpha}(-bc^{-1}) \cdot x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot s_0 \cdot h_{\beta - \alpha}(c^{-1}) = \\
 = x_{-\beta}(m'X) \cdot x_{\beta - \alpha}(-b) \cdot s_1 \cdot h_{\alpha-\beta}(c^{-1}) \cdot x_{\alpha-\beta}\left(\epsilon acm'\right) \cdot x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot s_0 \cdot h_{\beta - \alpha}(c^{-1}) = \\
 =  x_{\beta - \alpha}(-b) \cdot x_{-\beta}(m'X) \cdot x_{-\alpha}(-\epsilon bm'X) \cdot s_1 \cdot x_{\alpha-\beta}(\epsilon ac^{-1}m') \cdot x_{-\alpha}\left(\frac{cmX}{1+am}\right) \cdot s_0 =
\end{multline}
